---
title: "Homework3"
author: "Jiaqi Ma 3028009001"
date: "2/18/2021"
output: pdf_document
---

```{r}
segment=read.csv("/Users/majiaqi/Desktop/ISE535/HW3/segment.csv")
stock=read.csv("/Users/majiaqi/Desktop/ISE535/HW3/stockreturns.csv")
universities=read.csv("/Users/majiaqi/Desktop/ISE535/HW3/universities.csv")
```
1.
```{r}
# a)
t1=table("ownHome"=segment$ownHome,"subscribe"=segment$subscribe)
t1
# b)
headlines=c("ownNo","ownYes")
sub=t1[,2]
all=c(t1[1,1]+t1[1,2],t1[2,1]+t1[2,2])
d1=rbind(sub,all)
d1=data.frame(d1)
names(d1)=headlines
d1
sub/all
prop.test(sub,all,alt="greater",correct=F)
```
p-value=0.3927>0.05

The proportion of subscribers is the same between home owners and home renters.

2.
```{r}
# a)
cor(stock)
# b)
pca2=prcomp(stock)
pca2$rotation
```
a) JPM,Citibank and Wfargo are related. Shell and Exxon are related.
b) PC1=-0.2228228*JPM-0.3072900*Citibank-0.1548103*WFargo-0.6389680*Shell-0.6509044*Exxon

PC2=0.6252260*JPM+0.5703900*Citibank+0.3445049*WFargo-0.2479475*Shell-0.3218478*Exxon

3.
```{r}
# scale the dataframe
d3=universities[,c(2:7)]
d3=scale(d3,center=F,scale=T)
row.names(d3)=universities$University
# a)
pca3=prcomp(d3)
# eigenvalues
pca3$sdev^2
# rotation matrix, columns are eigenvectors
pca3$rotation
# b)
library(factoextra)
fviz_pca_biplot(pca3,repel=T,
                col.var="grey",
                habillage=universities$Funding)
```
TOP10 Universities: Caltech, Harvard, Princeton, Brown, Dartmouth, Stanford, Yale, MIT, Duke, UCBerkeley

Universities with more expenses: Caltech, JohnsHopkins

Expenses and Accept differentiate the public and private universities.